\tool

### 2017-11-20 paper/paper.tex
Start of introduction

\section{Introduction}
%Importance
Software contains many tools and features designed to make users more efficient and effective in their work. However, despite a wide availability of such useful tools many are often ignored or because users do not know of their existence.\\

Automated recommendation systems can help solve this problem... \\

But existing recommendations systems are ineffective... \\

Peer interactions and receptiveness are effective~\cite{vlhcc17}... \\

We created \tool~to solve this... \\

@@

To answer these questions, we conducted a study analyzing \tool~on five? popular open source Java projects to observe how many tool suggestions would be made based on past changes to the code base and how software developers reacted to receiving recommendations. This research makes the following contributions:\\

\begin{itemize}
\item We introduce the design and implementation of a novel automated recommendation system \tool~
\item We provide implications for future
\end{itemize}

>>>>

\section{Introduction}
%Importance
Software contains many tools and features designed to make users more efficient and effective in their work. However, despite a wide availability of such useful tools, many are often ignored or underutilized because users do not know of their existence. The amount of tools provided by applications is also continuing to increase, making it more difficult for users to discover helpful tools. This lack of awareness can lead to wasted time and billions of wasted dollars each year.

One area where worker effectiveness and efficiency is extremely important is the software industry. Software has permeated nearly every facet of our society and. Additionally, defects and errors in software cost companies millions of dollars to fix.

Automated recommendation systems can help solve this problem...

But existing recommendations systems are ineffective...

Peer interactions and receptiveness are effective~\cite{vlhcc17}...

We created \tool~to solve this... To evaluate the effectiveness of our approach, we studied the following research questions (RQs): \\

@@

To answer these questions, we evaluated our system on open source Java projects to observe how many tool suggestions would be made based on past changes to the code base and how software developers reacted to receiving recommendations. This research makes the following contributions:

\begin{itemize}
\item introduce the design and evaluation of \tool, a novel approach to improving tool discovery
\item provide implications for designing effective automated recommendation systems.
\end{itemize}
